\thispagestyle{empty}
\section*{Authorship Declaration}
I, Joe Barrett, confirm that this dissertation and the work presented in it are my own achievement.
\\\\
Where I have consulted the published work of others is always clearly attributed.
\\\\
Where I have quoted from the work of others, the source is always given. With the exception of such quotations this dissertation is entirely my own work.
\\\\
I have acknowledged all main sources of help.
\\\\
If my research follows on from previous work or is part of a larger collaborative research project I have made clear exactly what was done by others and what I have contributed myself.
\\\\
I have read and understand the penalties of academic misconduct.
\\\\
I also confirm that I have obtained informed consent from all people I have involved in the work in this dissertation following the school's ethical guidelines.
\vspace{2cm}\\
Signed:
\vspace{2cm}\\
Date:
\vspace{2cm}\\
Matriculation Number:
\newpage
\thispagestyle{empty}
\section*{Data Protection Declaration}
Under the 1998 Data Protection Act, The University cannot disclose your grade to an unauthorised person. However, other students benefit from studying dissertations that have their grades attached.
\\\\
Please sign your name below one of the options below to state your preference.
\vspace{3cm}\\
The University may make this dissertation, with indicative grade, available to others.
\vspace{3cm}\\
The University may make this dissertation available to others, but the grade may not be disclosed.
\vspace{3cm}\\
The University may not make this dissertation available to others.
\newpage