\documentclass[a4paper, 12pt, hidelinks]{article}

\usepackage[natbibapa]{apacite}
\bibliographystyle{apacite}
\usepackage{blindtext}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[ddmmyyyy]{datetime}
\usepackage{enumitem}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage[margin=1in]{geometry}
\usepackage[toc,acronym,nonumberlist]{glossaries}
\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage[none]{hyphenat}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage[table]{xcolor}
\usepackage{url}
\usepackage{verbatim}
\usepackage{pdflscape}
\usepackage{epstopdf}
\usepackage{tabularx}
\usepackage{minted}
\usepackage{todo}
\usepackage{multirow}
\usepackage{subcaption}

\setmainfont{Arial}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}

\lhead{Joe Barrett - 40117680}
\rhead{SOC10101 Honours Project}
\lfoot{}
\cfoot{}
\rfoot{\thepage}

\makeglossary
\loadglsentries{glossary}

\newlist{chapterList}{enumerate}{1}
\setlist[chapterList]{label=\bfseries Chapter \arabic* - }
\newenvironment{where}{\noindent{}where\begin{itemize}[label={}, nosep]}{\end{itemize}}

\begin{document}
	\urlstyle{same}
	\pagenumbering{roman}
	\setcounter{secnumdepth}{4}
	\setcounter{tocdepth}{3}
	\input{../Title/title.tex}
	\input{../Declaration/declaration.tex}
	\setcounter{page}{1}
	\begin{abstract}\noindent
		\todo{Write abstract}
	\end{abstract}
	\clearpage
	\tableofcontents
	\clearpage
	\listoftables
	\clearpage
	\listoffigures
	\clearpage
	\listoflistings
	\clearpage
%	\listofequations
%	\newpage
	\pagenumbering{arabic}
	\section{Introduction}
	\input{sections/background}
	\section{Literature Review}\label{sec:lit_review}
	\begin{comment}
	The purpose of this section is to introduce the concepts of mountain bike suspension setup and indicate why this may be difficult for a less knowledgeable individuals. It will then continue to identify and explain common image analysis techniques and how they may be applied to mountain bike suspension setup.
	\\\\
	The aim of this project is to produce an application which provides the user with a suggested suspension setup using image analysis. This literature review will cover the settings which the application may produce as well as 
	\end{comment}
	The aim of this project is to produce an application which will provide the user with a suggested suspension setup using image analysis techniques. This literature review will identify the various settings relating to mountain bike suspension as well as the intricacies surrounding rear suspension and why it can be difficult to setup for novice riders. It will then go on to highlight how image analysis is carried out and the various techniques which can be used in the context of this project. This review will hopefully shed light on the problem at hand and how the identified application is a viable solution.
	\input{sections/physics}
	\input{sections/imageanalysis}
	\input{sections/analysistechniques}
	\input{sections/analysis_and_sport}
	\input{sections/combining_suspension_analysis}
	\subsection{Conclusion}
	By identifying the key aspects and settings relating to mountain bike suspension and the common image analysis techniques this literature review has highlighted the processes which this project can utilise to complete its aims. By using this knowledge, the following sections will identify distinct methods which the project will use to produce the application and cover the results. \todo{revise}
	\clearpage
	\section{Methodology}
	\input{sections/methodology}
	\clearpage	
	\section{Results}
	\input{sections/results}
	\clearpage
	\section{Conclusions}
	\input{sections/conclusion}
	\clearpage
	\bibliography{bibliography}	
	\clearpage
	\printacronyms
	\printglossary[type=main]
	\clearpage
	\input{sections/appendicies}
		\todos
\end{document}